### 2016-04-24 TreeLevel.tex
remark about Wilson loop (still undone)
Passarino...

\section{Sparticle Production at Tree Level}

@@

\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}

@@

@@

@@

\caption{Tree level diagrams for $GG \to \tilde{q}\tilde{q}^\dagger$}

@@

\caption{Tree level diagrams for $qq \to \tilde{q}\tilde{q}$}

@@

\caption{Tree level diagrams for $q\overline{q} \to \tilde{g}\overline{\tilde{g}}$}

@@

\caption{Tree level diagrams for $GG \to \tilde{g}\overline{\tilde{g}}$}

@@

\caption{Tree level diagrams for $qG \to \tilde{q}\tilde{g}$}

@@

For NLO-corrections the results are expanded up to $\mathcal{O}(\epsilon)$. Furthermore the usual Mandelstam variables $s,t,u$ and the following modifications of them are used:

@@

\subsection{Partonic Cross Sections}
The leading order cross sections are
\begin{align}
\sigma(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
&+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
\sigma(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
& + \frac{\hat{g}_s^2 g_s^2}{16\pi s}  \left[ \left( -\frac{4}{3}-\frac{8m_-^2}{3s} \right)\beta_{\tilde{g}} + \left( \frac{8 m_{\tilde{g}}^2}{3s} + \frac{8m_-^4}{3s^2} \right) L_2 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{m_-^4 + m_{\tilde{q}}^2s} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
\sigma(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
\sigma(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
&+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right]
\end{align}
where the abbreviations 
\begin{align}
&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}} && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}}\nonumber\\
&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2 && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2}\nonumber\\
& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}} && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}\nonumber\\
& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa} && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}
\end{align}
are used\cite{Beenakker:1996ch}. In contrast to the MSSM no statistical factor $\frac{1}{2}$ is taken into account for gluino-antigluino production, as these particles are distinguishable in the MRSSM. Still in comparison to the MSSM cross section for the channel $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$ only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the part associated with an $t$ ($u$) channel squark is different. In the MRSSM either $\tilde{q}_L$ or $\tilde{q}_R$ is allowed whilst in the MSSM both squarks contribute to the $t$ ($u$) channel diagram.

\subsection{Hadronic Cross Section}
factorization (pictorial explanation in factorization paper chapter 1.4)
The hadronic cross section for the production of a final state $X$, e.g. $X = \tilde{q},\tilde{q}$, can be obtained by convolving the partonic cross section with the parton density function of the initial partons.
\begin{align}
\sigma^B(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B (ij \to X, s = x_ 1x_2 S).
\end{align}
As the production of the final state $X$ may proceed with various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
\begin{align}
\sigma^B(H_1 H_2 \to X) = \sum_{i,j} \sigma^B(i,j \to X).
\end{align}
refer to Kribs, Martin

>>>>

\section{Sparticle Production at Tree Level}
In this chapter the production of strongly interacting supersymmetric particles\footnote{The production of sgluons is excluded from the analysis as their mass will be chosen to be too large to produce them.} in the MRSSM is considered.

@@

%\caption{Tree level diagrams for $q\overline{q} \to \tilde{q}\tilde{q}^\dagger$}

@@

%\end{figure}
%\begin{figure}[!htbp]

@@

    \node at (0,0) {};
\begin{scope}[shift={(0,-1)}]

@@

%\caption{Tree level diagrams for $GG \to \tilde{q}\tilde{q}^\dagger$}

@@

%\caption{Tree level diagrams for $qq \to \tilde{q}\tilde{q}$}

@@

%\caption{Tree level diagrams for $q\overline{q} \to \tilde{g}\overline{\tilde{g}}$}

@@

%\caption{Tree level diagrams for $GG \to \tilde{g}\overline{\tilde{g}}$}

@@

\caption{Tree level diagrams for squark and gluino production at tree level in the MRSSM. The processes $GG \to \tilde{q}\overline{\tilde{q}}$ and $qG \to \tilde{q}\tilde{g}$ are identical to those of the MSSM. The processes $q\overline{q} \to \tilde{q}\tilde{\overline{q}}$ and $qq \to \tilde{q}\tilde{q}$ involve the production of less chiralities than in the MSSM. Also in the $q\tilde{q} \to \tilde{g}\overline{\tilde{g}}$ channel only half of the t-channel squark chiralities occur in the MRSSM.(Anti-)Gluino production via initial gluons $GG \to \tilde{g}\overline{\tilde{g}}$ proceeds via the same diagrams like in the MSSM but its cross section is twice as much in the MRSSM for gluino and antigluino are distinguishable particles.}

@@

For NLO-corrections the results are given in $D = 4 - 2\epsilon$ dimensions. Furthermore the usual Mandelstam variables $s,t,u$ and the following modifications of them are used:

@@

In view of the renormalization to be performed at the 1-loop level it has been distinguished between the gauge coupling $g_s$ from the gluon-quark-quark vertex and its supersymmetric analogue $\hat{g}_s$ from the gluino-squark-quark vertex.

\subsection{Partonic Cross Sections}
Having calculated the absolute squared Feynman amplitudes one obtains the partonic cross section via
\begin{align}
\frac{\mbox{d}^2 \sigma}{\mbox{d}t\ \mbox{d}u} =& \frac{K_{ab}}{s^2} \frac{\pi S_{\epsilon}}{\Gamma(1-\epsilon)} \left[ \frac{tu-m_1^2m_2^2}{\mu^2 s}\right]^{-\epsilon} \Theta(tu-m_1^2m_2^2)\nonumber\\
&\ \Theta(s-4m^2) \delta(s+t+u-m_1^2-m_2^2) \sum |\mathcal{M}|^2
\end{align}
The leading order cross sections are
\begin{align}
\sigma(q_i \overline{q}_j \to \tilde{q}\tilde{q}^\dagger) &= \delta_{ij}  \frac{g_s^4}{16\pi s} (n_f-1) \left[ \frac{4}{27} - \frac{16 m_{\tilde{q}}^2}{27s} \right]\nonumber\\
&+ \delta_{ij} \frac{g_s^2\hat{g}_s^2}{16\pi s}  \left[ \left( \frac{4}{27} + \frac{8 m_-^2}{27 s} \right)\beta_{\tilde{q}}  + \left( \frac{8m_{\tilde{g}}^2}{27s} + \frac{8m_-^4}{27s^2} \right)L_1 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} + \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma(GG \to \tilde{q}\tilde{q}^\dagger) &= \frac{(n_f-1) g_s^4}{16\pi s} \left[ \left(\frac{5}{24} + \frac{31 m_{\tilde{q}}^2}{12s}\right)\beta_{\tilde{q}} + \left( \frac{4m_{\tilde{q}}^2}{3s} + \frac{m_{\tilde{q}}^4}{3s^2} \right) \ln \frac{1-\beta_{\tilde{q}}}{1+\beta_{\tilde{q}}} \right]\\
\sigma(q_i q_j \to \tilde{q}\tilde{q}) &= \frac{\hat{g}_s^4}{16\pi s} \left[ -\frac{8}{9}\beta_{\tilde{q}} +  \left( -\frac{4}{9} - \frac{8m_-^2}{9s} \right)L_1 \right]\\
\sigma(q \overline{q} \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \frac{16}{9} + \frac{32m_{\tilde{g}}^2}{9s} \right] \beta_{\tilde{g}}\nonumber\\
& + \frac{\hat{g}_s^2 g_s^2}{16\pi s}  \left[ \left( -\frac{4}{3}-\frac{8m_-^2}{3s} \right)\beta_{\tilde{g}} + \left( \frac{8 m_{\tilde{g}}^2}{3s} + \frac{8m_-^4}{3s^2} \right) L_2 \right]\nonumber\\
& + \frac{\hat{g}_s^4}{16\pi s} \left[ \left( \frac{32}{27} + \frac{32 m_-^4}{m_-^4 + m_{\tilde{q}}^2s} \right)\beta_{\tilde{g}} - \frac{64m_-^2}{27s}L_2 \right]\label{eq:qqbar_to_sgsgbar}\\
\sigma(GG \to \tilde{g}\overline{\tilde{g}}) &= \frac{g_s^4}{16\pi s} \left[ \left( -6 - \frac{51 m_{\tilde{g}}^2}{2s} \right)\beta_{\tilde{g}} + \left( -\frac{9}{2} - \frac{18 m_{\tilde{g}}^2}{s} + \frac{18 m_{\tilde{g}}^4}{s^2} \right)\ln \frac{1-\beta_{\tilde{g}}}{1+\beta_{\tilde{g}}} \right]\\
\sigma(q G \to \tilde{q} \tilde{g}) &= \frac{g_s^2\hat{g}_s^2}{16\pi s} \left[ \frac{\kappa}{s}\left( -\frac{7}{9} - \frac{32 m_{-}^2}{9s} \right) + \left( -\frac{8m_-^2}{9s} + \frac{2m_{\tilde{q}}^2m_-^2}{s^2} + \frac{8 m_-^4}{9s^2} \right)L_3\right.\nonumber\\
&+\left. \left( -1-\frac{2m_-^2}{s} + \frac{2m_{\tilde{q}}m_-^2}{s^2} \right)L_4 \right]
\end{align}
where the abbreviations 
\begin{align}
&\beta_{\tilde{q}} = \sqrt{1-\frac{4 m_{\tilde{q}}^2}{s}} && \beta_{\tilde{g}} = \sqrt{1-\frac{4 m_{\tilde{g}}^2}{s}}\nonumber\\
&m_-^2 = m_{\tilde{g}}^2 - m_{\tilde{q}}^2 && \kappa = \sqrt{(s-m_{\tilde{g}}^2-m_{\tilde{q}}^2)^2-4m_{\tilde{g}}^2m_{\tilde{q}}^2}\nonumber\\
& L_1 = \ln \frac{s+2m_-^2 - s\beta_{\tilde{q}}}{s+2m_-^2 + s\beta_{\tilde{q}}} && L_2= \ln \frac{s - 2m_-^2 - s\beta_{\tilde{g}}}{s - 2m_-^2 + s\beta_{\tilde{g}}}\nonumber\\
& L_3 = \ln \frac{s - m_-^2 - \kappa}{s - m_-^2 + \kappa} && L_4= \ln \frac{s + m_-^2 - \kappa}{s + m_-^2 + \kappa}
\end{align}
are used\cite{Beenakker:1996ch}. In contrast to the MSSM no statistical factor $\frac{1}{2}$ is taken into account for gluino-antigluino production, as these particles are distinguishable in the MRSSM. Still in comparison to the MSSM cross section for the channel $q \overline{q} \to \tilde{g}\overline{\tilde{g}}$ only the first line in \ref{eq:qqbar_to_sgsgbar} is doubled up as the part associated with an $t$ ($u$) channel squark is different. In the MRSSM either $\tilde{q}_L$ or $\tilde{q}_R$ is allowed whilst in the MSSM both squarks contribute to the $t$ ($u$) channel diagram.

\subsection{Hadronic Cross Section}
factorization (pictorial explanation in factorization paper chapter 1.4 and Dissertori and Seymour, Marx page 24 below)
The hadronic cross section for the production of a final state $X$, e.g. $X = \tilde{q},\tilde{q}$, can be obtained by convolving the partonic cross section with the parton density function of the initial partons.
\begin{align}
\sigma^B_{\mathrm{Had}}(ij \to X) = \int \mbox{d}x_1 \mbox{d}x_2\ f_i(x_1) f_j(x_2)\ \sigma^B_{\mathrm{Part}} (ij \to X, s = x_ 1x_2 S).
\end{align}
As the production of the final state $X$ may proceed with various initial partons one has to sum over all possible possibilities arising from the initial hadrons $H_1$ and $H_2$:
\begin{align}
\sigma^B_{\mathrm{Had}}(H_1 H_2 \to X) = \sum_{i,j} \sigma^B_{\mathrm{Had}}(i,j \to X).
\end{align}
refer to Kribs, Martin
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.45]{figures/mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/mr=2_MSSM+MRSSM}
\end{center}
\end{figure}
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.45]{figures/rel_weights_mr=0,9_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=2_MSSM+MRSSM}
\end{center}
\end{figure}
\begin{figure}[!htpb]
\begin{center}
\includegraphics[scale=.45]{figures/mr=5_MSSM+MRSSM}
\includegraphics[scale=.45]{figures/rel_weights_mr=5_MSSM+MRSSM}
\end{center}
\end{figure}
